### 2022-07-21 main/chapter_2ljets.tex
correct and clarift some jetm modelling

A maximally crude display of the jet mass variable is given in
Figure~\ref{fig:2ljets_jetm_c1n2_600_0} for a benchmark C1N2 model in
the fast simulation, showing that most jets have small masses but that
a substantial fraction appear in a bump around $m(W)$.
To check that a similar bump exists in data and background simulations,
I conducted a study into single-lepton events to search for $\ttbar$ events
in which one top decays leptonically, and the other to a boosted hadronic $W$
boson that is reconstructed into a single small-radius jet.
Since our main samples require two leptons, this study required independent
inputs derived from different sources, so to reduce the required computing time
I opted to include only $\ttbar$ and single-top backgrounds.
To verify the origins of high-mass jets, partonic truth information is used
to label those events containing a $W$ boson decaying to two quarks that are
within $\Delta R < 0.4$ of the hardest reconstructed jet.
The resulting bump is visible in Figure~\ref{fig:2ljets_jetm_ttbar_mw} in a
selection described in its figure caption, and indeed contains the targetted
boosted $W$ boson. This positive result was an early motivation for our
continued pursuit of the 1J regions.

@@

% problem of jet mass for small radius
Our inclusion of SR-High-1J and VR-High-1J regions induces two related problems.
First is their unusual use of the jet mass variable $\mjetone$ with
small-radius ($R=0.4$), topologically clustered jets~\cite{atlas_jet_topo_PERF_2014_07}.
Usually, hadronic decays of massive objects
(such as $W$, $Z$, or $t$ resonances) are searched for with large-radius jets
with $R=0.8$, since these require less extreme boosts to capture their targets.
The focus from ATLAS' performance operations is therefore reasonably to
understand these common use-cases first.
Second is the use of fast simulation~\cite{SOFT-2010-01} for our signal models,
which uses approximate descriptions of the detector response and does not
guarantee to model the substructure that determines a jet's mass.

>>>>

A maximally crude display of the jet mass variable is given in
Figure~\ref{fig:2ljets_jetm_c1n2_600_0} for a benchmark C1N2 model, showing
that most  jets have small masses but that a substantial fraction appear in a
bump around $m(W)$.
However, all of our signal models are simulated with the fast ATLAS simulation
ATLFAST-II~\cite{SOFT-2010-01} that uses approximate descriptions of the
detector response and does not guarantee to accurately model the substructures
that determines the jet's reconstructed mass.
Jet mass modelling should be well described since masses are part of the
reconstructed energy, and so also for standard mass variables such as $\mjj$.
However, momenta are typically more important for these variables, so
errors could be hidden.
Inclusion of these 1J regions in the $\twoljets$-electroweak search therefore
required validation of these ATLFAST-II mass distributions.

To check that a similar bump exists in data and fully simulated (FullSim)
background simulations, I conducted a study into a standard model process
production boosted hadronic $W$ bosons in $\ttbar$ events.
Although non-$\ttbar$ $WW$ processes do occur, the semileptonic $\ttbar$
process additionally produces two $b$ quarks in its dominant decay, and their
$b$-tagged jets that can be selected to reduce backgrounds.

Since our main samples require two leptons, this study required independent
single-lepton inputs derived from different sources, so to reduce the required
computing time I included only $\ttbar$ and single-top backgrounds generated
with the full \atlas simulation.
To verify the origins of high-mass jets, partonic truth information is used
to label those events containing a $W$ boson decaying to two quarks within
$\Delta R < 0.4$ of the hardest reconstructed jet.
The resulting bump does exist, as shown in
Figure~\ref{fig:2ljets_jetm_ttbar_mw}.
This positive result was an early motivation for our continued pursuit of the
1J regions.

@@

% problem of jet mass for small radius
Not only does fast simulation pose a problem to the 1J regions, but our use
of $\mjetone$ in small-radius ($R=0.4$), with the older
`topologically clustered' jet technology~\cite{atlas_jet_topo_PERF_2014_07}
is also unusual.
% TODO citations for large-R jet searches
Hadronic decays of massive objects
(such as $W$, $Z$, or $t$ resonances) in \atlas are usually searched for with
large-radius jets with $R=0.8$, since these require less extreme boosts to
capture their targets.
The focus from ATLAS' performance operations is therefore reasonable to
understand these common use-cases first.
